The pollination trade-off

### 2018-11-29 paper/manuscript.Rmd
Add discourse of random effects and improve start of paragraph quest. 2

Our models of pollen deposition had relatively high explanatory power. 
The conditional coefficient of determination R^2^~(c)~ [@nakagawa_general_2013] for the most parsimonious models (those with the lowest AICc) ranged between `r r2_values$r2c_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "conspecific_abs"]`) for the models of conspecific pollen and between `r r2_values$r2c_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the models of heterospecific pollen. 
A large portion of the explanatory power came from the random effects, in particular for the conspecific pollen models. 
Indeed, the marginal coefficient of determination R^2^~(m)~, which describes the proportion of variance explained for the fixed variables alone, ranged between `r r2_values$r2m_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "conspecific_abs"]`) for the conspecific models and between `r r2_values$r2m_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the heterospecific models.
By examining the AICc scores of a set of linear mixed effect models, we found that the visit efficay and the plants abbundance were the most important ecological variables predicting the amount of conspecific and heterospecific pollen deposited in the plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a). 
The plants functional originality had an intermediate importance, while, surprisingly, the number of shared pollinators was comparatively less unimportant as it was only included in models with relatively large AICc values.

>>>>

Using a set of LMM, we then examined the role that four ecological variables play on pollen deposition and, by extension, in the quantity and quality of pollination. 
We found that our models of pollen deposition had relatively high explanatory power. 
The conditional coefficient of determination R^2^~(c)~ [@nakagawa_general_2013] for the most parsimonious models (those with the lowest AICc) ranged between `r r2_values$r2c_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "conspecific_abs"]`) for the bootstrap replicates of theconspecific pollen models and between `r r2_values$r2c_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the models of heterospecific pollen. 
A large portion of the explanatory power came from the random effects, in particular for the conspecific pollen models. 
Indeed, the marginal coefficient of determination R^2^~(m)~, which describes the proportion of variance explained for the fixed variables alone, ranged between `r r2_values$r2m_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "conspecific_abs"]`) for the conspecific models and between `r r2_values$r2m_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the heterospecific models. 
As determined by the AICc, the random structure best supported by the data was the one that fits an intercept for each species in a community independently (as opposed to an intercept for each species irrespective of the community they belong to). 
This was so for both the models of conspecific and heterospecific pollen (Table SXX).
